A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-31 paper.tex
gah

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
 & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
 \multirow{4}*{$(2,2)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
 \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (\gg \otimes \CC^{\mc N_- -2})/\gg)$} & \\  \hline
 \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, U \ham \gg)$} & \\  \hline
 \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
 \label{table_of_twists_2d}
\end{table}

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^*\wedge B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
\end{align*}
\end{prop}

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{BF} + \int\dvol\left(-t(b, A_{0, 1}^*) + t a c^* + \frac{t}{2} \xi^*\wedge B^* + t (\varphi, \phi^*) + \frac t4 (\psi^*, \psi^*) \right),\]
where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4dholomorphictwist})
\[
\xymatrix@R=0.5cm@C=0cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varphi^*} \\
& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

\begin{prop}
Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}. The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
\begin{align*}
I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
\end{align*}
\end{prop}

@@

\begin{proof}
We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
\begin{align*}
& (t \varphi, \rho, t \phi, A_{1,0}) \\
& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
\end{align*}
This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
\begin{align*}
\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] -[\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( + t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\wt\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
\end{align*}

@@

\begin{proof}
On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.  We can then enhance this identifying the fields, as $\ZZ$-graded $\mr U(1)$ with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.  When we calculate that dimensional reduction the fields reduce according to the rule
\begin{align*}
\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes \gg[k] \oplus \gg[k-1] \\
&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR\otimes (\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2]).
\end{align*}
Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
\end{proof}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sect:2d(2,2)}
First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  The R-symmetry group is $CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.

@@

In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.  There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$.  
 \item Square-zero supercharges of rank $(1,1)$ are topological, and split into two orbits under $\spin(2;\RR) \times G_R$: acting by $G_R$, we can \chris{...}. The B-supercharge
 \item 
\end{itemize}

@@

@@

@@

@@

@@

@@

@@

>>>>

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c}
 $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{6}*{$(4,4)$} & \multirow{2}*{\hyperref[sect:2d44minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{Dol}})$} & \\ \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, U \ham \gg)$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d44Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (U \ham \gg)_{\mr{dR}})$} & \\  \hline
 \multirow{6}*{$(2,2)$} & \multirow{2}*{\hyperref[sect:2d22minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Dol}})$} & \\  \cline{2-4}
  & \multirow{2}*{\hyperref[sect:2d22Btwist] {Rank $(1,1)$ (B)}} & {Topological BF theory coupled to $R$ matter} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\RR^2_{\mr{dR}}, (R/\gg))$} & \\  \cline{2-4}
 & \multirow{2}*{\hyperref[sect:2d22Atwist] {Rank $(1,1)$ (A)}} & {Perturbatively trivial (A-model)} & \multirow{2}*{2 (topological)} \\
 && {$T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{dR}})$} & \\  \hline
 \multirow{2}*{$(0,\mc N_-)$} & \multirow{2}*{\hyperref[sect:2d0Nminimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $\mc N_- - 2$ free fermions} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, (\gg \otimes \CC^{\mc N_- -2})/\gg)$} & \\  \hline
 \multirow{2}*{$(0,4)$} & \multirow{2}*{\hyperref[sect:2d04minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to a holomorphic symplectic boson} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, U \ham \gg)$} & \\  \hline
 \multirow{2}*{$(0,2)$} & \multirow{2}*{\hyperref[sect:2d02minimaltwist] {Rank $(1,0)$}} & {Holomorphic BF theory coupled to $R$ matter} & \multirow{2}*{1 (holomorphic)} \\
 && {$T^*[-1]\mr{Map}(\CC, R/\gg)$} & \\ \hline
 \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories in two dimensions with gauge group $G$.  When $\mc N=(0,2)$ and $(2,2)$ the theory includes a chiral multiplet valued in a representation $R$. When $\mc N=(0,4)$ and $(4,4)$ the theory includes a hypermultiplet valued in a symplectic representation $U$.}
 \label{table_of_twists_2d}
\end{table}

@@

\begin{prop}
Suppose $Q_t$ is the rank $(2,0)$ supercharge of \ref{eq:4dHodgefamily}.
The $\MU(2)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 4d $\cN=2$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - t(b, A_{0, 1}^*) - (\wt \chi + t\chi)\wt a^*\right) \\
& + \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1}  + [a, \wt a])\chi^* + [\phi, \phi]\xi^* \right) \\
&+ \int\dvol\left( t\Omega^{-1} F_{2, 0}\wedge B^* + (t\dd_{A_{1, 0}} a, \rho^*)\right) \\
%&+ \int\dvol\left((F_{0, 2}, B^*) + t\Omega^{-1} F_{2, 0}\wedge B^* + (\ol\dd_{A_{0, 1}}a, b^*) + (t\dd_{A_{1, 0}} a, \rho^*) + \frac{1}{2}\Lambda F_{1, 1}(\chi^* - t\wt\chi^*)\right) \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol \left(t\chi^*\wt \chi^* + \frac{t}{2} \xi^* B^* -\frac{1}{4}(\chi^* + t\wt\chi^*)^2 + t a c^*\right) \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol \left((\Tilde{\nu}, \nu^*) + t (\varphi, \phi^*) + [\phi, \nu] + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*) + [\nu, a]\varphi^* \right) \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol \frac t4  (\psi^*, \psi^*)
\end{align*}
\end{prop}

%The $(1,2)$ action is in comments, it should agree with the $t=0$ limit of the above.
%\begin{align*}
%I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
%&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
%&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
%I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
%\end{align*}

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4dholomorphictwist})
\[
\xymatrix@R=0.5cm@C=0cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varphi^*} \\
& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

\begin{prop}
Suppose $Q_t$ is the rank $(1,2)$ supercharge of \eqref{eq:4d412Hodgefamily}. The $\MU(2)$ decomposition of the functionals $I^{(1)}, I^{(2)}$ (see \eqref{eq:gaugeI1}, \eqref{eq:gaugeI2}) in terms of the fields of 4d $\cN=4$ super Yang--Mills theory are
\begin{align*}
I^{(1)}(Q_t) &= \int \dvol\left(-(\rho, A_{1, 0}^*) - \wt \chi\wt a^* - (\Tilde{\nu}, \nu^*) - t(\varphi, A_{1, 0}^*) - t(\wt\nu, A_{0, 1}^*) - t(b, \nu^*) - t(\rho, \phi^*) - t(\Lambda\psi)\wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} + [\phi, \nu] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* + [\nu, a]\varphi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
&+t\int\dvol\left(\frac{1}{2} (F_{1, 1} + [\phi, \nu] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* + \Lambda \dd_{A_{1, 0}}\nu \chi^* + \dd_{A_{1, 0}} a \varphi^* + \ol\dd_{A_{0, 1}} a \wt\nu^* + [\phi, a]\rho^* + [\nu, a]b^*\right) \\
I^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right) \\
\end{align*}
\end{prop}

@@

\begin{proof}
We begin by applying Corollary \ref{cor: quad} to the two $t$-dependent quadruples of fields:
\begin{align*}
& (t \varphi, \rho, t \phi, A_{1,0}) \\
& (tb, \Tilde{\nu}, t A_{0,1}, \nu) .
\end{align*}
This has the effect of integrating out the fields $(\rho, A_{1,0})$ and $(\Tilde{\nu}, \nu)$ and replaces the action functionals by
\begin{align*}
\Tilde{I}^{(1)}(Q_t) &= \int \dvol\left(- t^2 (\varphi, \phi^*) - t^2 (b, A_{0, 1}^*) - (\wt \chi + t\Lambda\psi) \wt a^*\right) \\
&+ \int\dvol\left((F_{0, 2}, B^*) + (\ol\dd_{A_{0, 1}}a, b^*) + \frac{1}{2}\Lambda(F_{1, 1} - t [\phi, A_{0,1}] + \omega [a, \wt a])\chi^* + [\phi, \phi]\xi^* - t [A_{0,1}, a] \phi^* + \frac{1}{2} (\dbar_{A_{0,1}} \phi, \psi^*)\right) \\
%&+t\int\dvol\left(\frac{1}{2} (-t \dbar \phi + \partial A_{0,1} -t [\phi, A_{0,1}] + \omega\wedge [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
&+t\int\dvol\left(\frac{1}{2} (F_{1,1} -t [\phi, A_{0,1}] + \omega [a, \wt a], \psi^*) + \Lambda \ol\dd_{A_{0, 1}} \phi \wt\chi^* - t^2 \Lambda \partial_{\phi} A_{0,1} \chi^* - t \partial_\phi a \varphi^* \right) \\ & + t \int \dvol \left( t \dbar_{A_{0,1}} a b^* + t [\phi, a] \varphi^* - t [A_{0,1}, a]b^* \right) \\
\Tilde{I}^{(2)} (Q_t, Q_t) &= \int \dvol \left(t^2(\xi^*B^* + \chi^*\wt\chi^* + \frac{1}{2}(\psi^*, \psi^*)) -\frac{1}{4}(\chi^* + t \Lambda\psi^*)^2 + t^2 ac^*\right)
\end{align*}

The next step is to decompose the $(1,1)$ form $\psi$ as
\[
\psi = \omega \Lambda \psi + \psi_{\perp}
\]
where $\Lambda \psi_{\perp} = 0$.

@@

\begin{proof}
On the level of $\ZZ/2\ZZ$-graded theories, we apply the forgetful map from $\mc N=8$ super Poincar\'e action down to the $\mc N=4$ super Poincar\'e action and then apply Theorem \ref{3d_4_minimal_twist_thm}.  We can then enhance this identifying the fields with the dimensional reduction of the fields from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills, as a $\ZZ$-graded vector bundle equipped with a $\mr U(1)$-equivariant structure.  The dimensionally reduced theory is a $\ZZ$-graded and $\mr U(1)$-equivariant theory, equivalent as a $\ZZ/2\ZZ$-graded theory to the one obtained from 3d $\mc N=4$ -- this promotes the description given above to a $\ZZ$-graded and $\mr U(1)$-equivariant theory.  When we calculate that dimensional reduction, the fields reduce according to the rule
\begin{align*}
\Omega^{\bullet,\bullet}(\CC^2) \otimes \gg[k] &\mapsto \Omega^{\bullet,\bullet}(\CC) \otimes \Omega^\bullet(\RR) \otimes (\gg[k] \oplus \gg[k-1 \\
&\iso \Omega^{0,\bullet}(\CC)\otimes \Omega^\bullet(\RR) \otimes ((\gg[k] \oplus \gg[k-1]) \oplus (\gg[k-1] \oplus \gg[k-2])).
\end{align*}
Starting from the fields of Theorem \ref{3d_4_minimal_twist_thm}, we obtain -- $\mr U(1)$-equivariantly -- the desired fields with their correct $\ZZ$-gradings.
\end{proof}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sect:2d(2,2)}
First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.

@@

In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.  There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$.  
 \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times G_R$.  Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors $((\lambda, \pm i \lambda), (\mu, \pm i \mu)) \in W_+ \oplus W_-$ with $\lambda, \mu \ne 0$.  By acting by $G_R$ we can set $\lambda = \mu = 1$, leaving four orbits, represented by the supercharges $Q_A = ((1,i),(1,i)), Q_A^\dagger = ((1,-i),(1,-i)), Q_B = ((1,i),(1,-i))$ and $Q_B^\dagger = ((1,-i),(1,i))$.  The two A-supercharges are compatible with the A-twisting homomorphism $\phi_{A} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$, and the two B-supercharges are compatible with the B-twisting homomorphism $\phi_{B} \colon \spin(2;\CC) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,-1)$.  Moreover, the A-supercharges can be promoted to twisting data using the homomorphism $\alpha_A = \phi_B$, and the B-supercharges can be promoted to twisting data using $\alpha_B = \phi_A$.
\end{itemize}

@@

\subsubsection{Minimal Twist} \label{sect:2d22minimaltwist}

@@

\subsubsection{Topological A Twist} \label{sect:2d22Atwist}

@@

\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
\subsubsection{Topological A Twist} \label{sect:2d44Atwist}

@@

\subsubsection{Topological B Twist} \label{sect:2d44Btwist}

@@

\subsubsection{Minimal Twist} \label{sect:2d02minimaltwist}

@@

\subsubsection{Minimal Twist} \label{sect:2d04minimaltwist}

@@

\subsubsection{Minimal Twist} \label{sect:2d0Nminimaltwist}
